---
title: 'Steal like an Rtist: Creative Coding in R'
subtitle: '02 - Homage to the Square Exercise 1'
output: html_document
---

# Exercise 1

## Part 1

Update the function `make_homage()` to take a `seed` argument, and set the seed in the body of the function

```{r ex-1-1}
library(ggplot2)
library(dplyr)
library(patchwork)

make_homage <- function(
    seed = 1,
    colors = c("#5A9CBA", "#919EA3", "#F1EFDF", "#F5BB1D")
  ) {
  set.seed(seed)
  
  tribble(
    ~x0, ~y0, ~size,
    0, 0, 10,
    1, 0.5, 8,
    2, 1, 6,
    3, 1.5, 4
  ) %>%
    mutate(
      x1 = x0 + size,
      y1 = y0 + size,
      color = sample(colors, size = 4)
    ) %>%
    ggplot() +
    geom_rect(aes(
      xmin = x0, xmax = x1,
      ymin = y0, ymax = y1,
      fill = color
    )) +
    scale_fill_identity() +
    coord_fixed(expand = FALSE) +
    theme_void()
}

make_homage(19091991, colors = c("#5F187F", "#FF823E", "#FFFFE0", "#B486D4"))
```

What happens if there is no value given to `seed` in the function?

```{r ex-1-2}
make_homage()
```

## Part 2

Verify that running `make_homage()` with the same `seed` creates the same output, and that with a different seeds creates different outputs

```{r ex-1-3}
mh1 <- make_homage(19091991, colors = c("#5F187F", "#FF823E", "#FFFFE0", "#B486D4"))
mh2 <- make_homage(19, colors = c("#5F187F", "#FF823E", "#FFFFE0", "#B486D4"))
mh3 <- make_homage(91, colors = c("#5F187F", "#FF823E", "#FFFFE0", "#B486D4"))
mh4 <- make_homage(9, colors = c("#5F187F", "#FF823E", "#FFFFE0", "#B486D4"))

(mh1 + mh2) / (mh3 + mh4)

```

## Part 3

Share an output and the seed that created it in the GitHub discussion for this exercise! https://github.com/posit-conf-2023/creative-coding/discussions/2

Inspiration was Klimt's The Kiss

```{r ex-1-4}
library(glue)

klimt_kiss <- c('#7c6739', '#ca8d32', '#8f6d2c', '#81682d', '#f2b949')

klimt_seed <- 1919
klimt_homage <- make_homage(klimt_seed, colors = klimt_kiss)

klimt_homage

ggsave(
  filename = here::here(
    'steal-like-artist', 
    "images", 
    glue("homage_klimt_{klimt_seed}.png")
  ),
  plot = klimt_homage,
  width = 5, height = 5
)
```

Inspiration was Hokusai's The Great Wave off Kanagawa

```{r ex-1-5}

great_wave <- c('#080d53', '#c5bfae', '#e7cdab', '#86a8b4', '#686450')

wave_seed <- 91911
wave_homage <- make_homage(wave_seed, colors = great_wave)

wave_homage

ggsave(
  filename = here::here(
    'steal-like-artist', 
    "images", 
    glue("homage_great_wave_{wave_seed}.png")
  ),
  plot = wave_homage,
  width = 5, height = 5
)
```
